---
title: "p8105_hw1_stl2137.Rmd"
output: github_document
---

```{r, include = FALSE}
library(tidyverse)
```

# Homework 1 Problem 1

## Creating the dataframe request in question 1
```{r}
hw1q1_df <- tibble(
  random_normsample = rnorm(8),
  pos_random_normsample = as.logical(random_normsample > 0), 
  charac_vector = as.character("a", "b", "c", "d", "e", "f", "g", "h"),
  factor_vector = as.factor(c(1, 1, 2, 3, 2, 1, 2, 3)) 
)

mean(hw1q1_df$random_normsample)
mean(hw1q1_df$pos_random_normsample)
mean(hw1q1_df$charac_vector)
mean(hw1q1_df$factor_vector)
```
Arguments that are not numeric or logical, such as character or factor arguments, will return NA, as seen by the error messages incurred above.

### Applying the as.numeric function to the logical, character, and factor variables:
```{r, eval = FALSE}
num_pos_random_normsample <- as.numeric(hw1q1_df$pos_random_normsample)
num_charac_vector <- as.numeric(hw1q1_df$charac_vector)
num_factor_vector <- as.numeric(hw1q1_df$factor_vector)
```
By utilizing `as.numeric`, we are changing the class of the variables from their original form to numeric. This enables us to calculate the mean of numbers. In my specific case, there is still an error when I use `as.numeric(hw1q1_df$charac_vector)` because my character vector is comprised of letters, which cannot be averaged.

```{r}
# Logical vector to numeric, multiply random sample by result
num_pos_random_normsample <- as.numeric(hw1q1_df$pos_random_normsample)
num_pos_random_normsample*hw1q1_df$random_normsample

# Logical vector to factor, multiply random sample by result
fac_pos_random_normsample <- as.factor(hw1q1_df$pos_random_normsample)
fac_pos_random_normsample*hw1q1_df$random_normsample

#Logical vector to factor, convert result to numeric, multiple random sample by result
num_fac_pos_random_normsample <- as.numeric(fac_pos_random_normsample)
num_fac_pos_random_normsample*hw1q1_df$random_normsample
```

